Routines and Regret: An Examination of Behavioral Norms and Emotional Responses

### 2024-02-15 paper/paper.qmd
modify

# References

>>>>

# References
@tellingstories
@bear2017normality
@briazu2017undoing
@buck1994reactions
@byrne2016counterfactual
@chandler2014nonnaivete
@cialdini2003crafting
@dixon2011if
@epstein1992irrational
@epstude2008functional
@feldman2018what
@feldman2017norm
@gavanski1989counterfactual
@guttentag2004reality
@hooker2000impoverished
@hur2009regrets
@kahneman1986norm
@kahneman1982simulation
@koehler2003normality
@koonce2015effects
@mceleney2006spontaneous
@miller1986counterfactual
@miller1991gender
@miller1989coincidence
@miller1990counterfactual
@ngbala1997action
@roese1997counterfactual
@roese2017functional
@roese1997affective
